A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
New abstract

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive haloes have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive haloes have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger haloes have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation. 
    \song{This is the abstract of old draft, need some works}

>>>>

    In \citet{hscMassiveI}, we use deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) images of ${\sim}3000$ massive (\mstar{}$\geq 11.5$) central 
    galaxies at $0.3 < z < 0.5$ from the Hyper Suprime-Cam Subaru Strategic Program 
    to show that more massive central galaxies display more prominent stellar haloes 
    with shallower outer stellar mass density profile (\mden) and higher ellipticity. 
    In this work, we investigate the environment dependence of stellar mass 
    distributions of massive central galaxies using the same dataset.
    Treating stellar mass within a 100 kpc elliptical aperture (\mtot{}) as proxy of 
    total stellar mass, we show that at fixed \mtot{}, massive central galaxies in 
    \mhalo{}$\geq 10^{14}$\msun{} haloes show slightly shallower \mden{} profiles, 
    larger half-light radius, and lower fraction of stellar mass within inner 10 kpc 
    (\minn{}) than the centrals of \mhalo{}$< 10^{14}$\msun{} haloes. 
    At fixed \minn{}--a tracer of the \textit{in situ} stellar mass, central galaxies 
    from more massive haloes host much more significant outer stellar haloes despite 
    their inner \mden{} profiles are very similar with the ones in less massive haloes.
    These results clearly demonstrate that mass--size relation for central galaxies 
    indeed depends on environment at high-\mtot{} end. 
    We also show that the \mtot{}--\minn{} relation can reflect this dependence 
    better and can help diagnose the assembly of massive galaxies and their haloes.
    These results suggest more massive haloes favor more efficient growth of stellar 
    haloes in their central galaxies, which is broadly consistent with the two phase 
    formation scenario of massive galaxies in which their outer envelopes are 
    accumulated through accretions of small systems.
